PyPy's Approach to Virtual Machine Construction

### 2006-05-31 talk/dls2006/paper.tex
LL = low-level

Finally, currently under development is a variant of the very first
transformation step, for use when targeting higher-level,
object-oriented (OO) environments.  It is currently being designed
together with back-ends for Smalltalk/Squeak\footnote{Our simple OO
type system is designed for \textit{statically-typed} OO environments,
including Java; the presence of Smalltalk as a back-end might be
misleading in that respect.} and CLI/.NET.  This first transformation
step, for C-like environments, is called the \textit{LLTyper}: it produces
C-level flow graphs, where the object-oriented features of RPython
(classes and instances) become manipulations of C structs with
explicit virtual table pointers.  By contrast, for OO environments the
transformation step is called the \textit{OOTyper}: it targets a simple
object-oriented type system, and preserves the classes and instances
of the original RPython program.  The LLTyper and OOTyper still have
much code in common, to convert the more Python-specific features like
its complex calling conventions.

>>>>

Finally, currently under development is a variant of the very first
transformation step, for use when targeting higher-level,
object-oriented (OO) environments.  It is currently being designed
together with back-ends for Smalltalk/Squeak\footnote{Our simple OO
type system is designed for \textit{statically-typed} OO environments,
including Java; the presence of Smalltalk as a back-end might be
misleading in that respect.} and CLI/.NET.  This first transformation
step, for C-like environments, is called the \textit{LLTyper} or
low-level typer: it produces
C-level flow graphs, where the object-oriented features of RPython
(classes and instances) become manipulations of C structs with
explicit virtual table pointers.  By contrast, for OO environments the
transformation step is called the \textit{OOTyper}: it targets a simple
object-oriented type system, and preserves the classes and instances
of the original RPython program.  The LLTyper and OOTyper still have
much code in common, to convert the more Python-specific features like
its complex calling conventions.
